Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.tex

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden]}{\end{tcolorbox}}\fi

@@

The split between training and validation conditions was selected to
achieve a large difference in fluxes between the two categories. The
split was determined as we are interested in showing how our model can
fit to varied conditions, and conditions closer to the training set are
likely to be predicted well without necessarily learning the system.

@@

The prior distributions and corresponding true parameter values used in
our case study are shown in supporting information section 3.2. They
were chosen to reflect a plausible pre-experimental information state.
In 7 cases, the marginal prior distribution for a parameter disagrees
with the true parameter values used to generate the data; a similar
situation is likely to occur in practice due to \emph{in vivo} vs
\emph{in vitro} measurement differences.

>>>>

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, enhanced, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden]}{\end{tcolorbox}}\fi

@@

The training testing split was selected to achieve a large difference
between the fluxes of the training and testing dataset. The split was
determined as we are interested in showing how our model can fit to
varied conditions, and conditions closer to the training set are likely
to be predicted well without necessarily learning the system.

@@

The prior distributions and corresponding true parameter values used in
our case study are shown in supporting information section 3.2. They
were chosen to reflect a plausible pre-experimental information state.
In 7 cases, the marginal prior distribution for a parameter disagrees
with the true parameter values used to generate the data. A similar
situation is likely to occur in practice due to \emph{in vivo} vs
\emph{in vitro} measurement differences.
